Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-10-05 Asymptomatic_LSR_Supplement.Rmd
Update
Update

#arrange by number of studies
Q1_table_countries <- Q1_table_countries %>%
  arrange(desc(n))

@@

## Flowchart
*In progress.*

@@

## Review question 1, sensitivity analysis, omitting studies that were preprints at the time of literature search.
![Figure 3. Review question 1, sensitivity analysis, omitting studies that were preprints at the time of literature search](forest_meta_Q1_published.png)

>>>>

#arrange by number of studies
Q1_table_countries <- Q1_table_countries %>%
  arrange(desc(n))
#create PRISMA 2020 flowchart

#download packages
library(devtools)
library(dplyr)
install_github("nealhaddaway/PRISMA2020")

#create df from example csv file
PRISMA <- read.csv("PRISMA.csv")

#set the REDCap IDs
#last REDCap ID in previous version
last_ID_prev <- 1000
#last REDCap ID in current version
last_ID_current <- 5296
#load all records in redcap

# get the data directly from redcap:
url <- "https://redcap.ispm.unibe.ch/api/"
token <- "F2725F15FE84D2832E2793BB23B0A62B"
formData <- list("token"=token,
                 content='report',
                 format='csv',
                 report_id='158',
                 csvDelimiter='',
                 rawOrLabel='raw',
                 rawOrLabelHeaders='raw',
                 exportCheckboxLabel='false',
                 returnFormat='csv'
)
response_all <- httr::POST(url, body = formData, encode = "form")
all_records <- httr::content(response_all)

#find number of studies identified in databases since previous update
current_records <- all_records[last_ID_prev:last_ID_current, ]
PRISMA$n[PRISMA$data == "database_results"] <- nrow(current_records[!is.na(current_records$record_id), ]) - 1 #1 was added manually 9484

#find number included in review
PRISMA$n[PRISMA$data == "new_studies"] <- nrow(current_records %>% filter(review == 1))

#find number of duplicates removed before screening
PRISMA$n[PRISMA$data == "duplicates"] <- nrow(current_records %>% filter(ex_reas == 14))
#find number of records screening
PRISMA$n[PRISMA$data == "records_screened"] <- nrow(current_records) - 
  nrow(current_records %>% filter(ex_reas == 14))
#add number of studies found via other methods 
#1 study #9484 was added manually - it's the published v of a preprint
#as a result, I need to minus 1 record from the database result
PRISMA$n[PRISMA$box == "othstud"] <- 1

#find number of records excluded from title and abstract
PRISMA$n[PRISMA$data == "records_excluded"] <- nrow(current_records %>% filter(ex_reas == 1))
check <- current_records %>% filter(ex_reas == 1)
#current records left after title and abstract screening
full_text_screen <- current_records %>% filter(ex_reas != 14 & ex_reas != 1)

#find number of full texts retrieved
PRISMA$n[PRISMA$data == "dbr_sought_reports"] <- nrow(current_records) - 
  (nrow(current_records %>% filter(ex_reas == 14)) + 
  nrow(current_records %>% filter(ex_reas == 1)))

#find number of full texts screened
PRISMA$n[PRISMA$data == "dbr_assessed"] <- nrow(current_records) - 
  (nrow(current_records %>% filter(ex_reas == 14)) + 
     nrow(current_records %>% filter(ex_reas == 1)))

#find number included in previous version
prev_records <- all_records[1:last_ID_prev, ]
PRISMA$n[PRISMA$data == "previous_studies"] <- nrow(prev_records[prev_records$review == 1, ])

#calculate total studies included
PRISMA$n[PRISMA$data == "total_studies"] <- nrow(prev_records[prev_records$review == 1, ]) +
  nrow(current_records[current_records$review == 1, ])

# studies excluded
excl_11 <-  nrow(current_records %>% filter(ex_reas == 11))
excl_12 <-  nrow(current_records %>% filter(ex_reas == 12))
excl_13 <-  nrow(current_records %>% filter(ex_reas == 13))
excl_15 <-  nrow(current_records %>% filter(ex_reas == 15))
excl_16 <-  nrow(current_records %>% filter(ex_reas == 16))
excl_17 <-  nrow(current_records %>% filter(ex_reas == 17))
excl_19 <-  nrow(current_records %>% filter(ex_reas == 19))
excl_20 <-  nrow(current_records %>% filter(ex_reas == 20))
excl_21 <-  nrow(current_records %>% filter(ex_reas == 21))
excl_18 <-  nrow(current_records %>% filter(ex_reas == 18))

excl_reasons <- paste0("Publication not on COVID-19, ", excl_11, 
                       "; No original data, ", excl_12, 
                       "; Data included in other publication, ", excl_13, 
                       "; Insufficient extractable data, ", excl_15, 
                       "; Study design inappropriate, ", excl_16, 
                       "; No PCR/serological test, ", excl_17, 
                       "; Math. model not in review scope, ", excl_19, 
                       "; Inadequate follow-up time, ", excl_20, 
                       "; Preprint of published article, ", excl_21, 
                       "; Other, ", excl_18)
excl_reasons
PRISMA$n[PRISMA$data == "dbr_excluded"] <- excl_reasons

#fix some text in the flowchart data
PRISMA$boxtext[PRISMA$data == "identification"] <- "Identification"
PRISMA$boxtext[PRISMA$box == "prevstud"] <- "Previous studies"

#read data
flowchart <- PRISMA2020::PRISMA_data(PRISMA)
flowchart
#generate flowchart
PRISMA2020::PRISMA_flowdiagram(data = flowchart, other = FALSE)
flowchart_plot <- PRISMA2020::PRISMA_flowdiagram(data = flowchart, other = FALSE)

PRISMA2020::PRISMA_save(flowchart_plot, filename = "PRISMA2020_flowdiagram.png", filetype = "png", overwrite = TRUE)

@@

## PRISMA 2020 Flowchart
![Figure 3. PRISMA 2020 Flow Diagram](PRISMA2020_flowdiagram.png)
***

@@

## Review question 1, sensitivity analysis, omitting studies that were preprints at the time of literature search.
![Figure 4. Review question 1, sensitivity analysis, omitting studies that were preprints at the time of literature search](forest_meta_Q1_published.png)

### 2021-10-05 Manuscript_draft.Rmd
Update
Update

#clean settings
Q1_table <- Q1_table %>%
  mutate(setting = ifelse(setting2 == 1, "Contact investigation", setting),
         setting = ifelse(setting2 == 2, "Contact investigation, aggregated", setting),
         setting = ifelse(setting2 == 3, "Outbreak investigation", setting),
         setting = ifelse(setting2 == 4, "Statistical model", setting),
         setting = ifelse(setting2 == 5, "Screening", setting),
         setting = ifelse(setting2 == 6, "Hospitalised adults", setting),
         setting = ifelse(setting2 == 7, "Hospitalised children", setting),
         setting = ifelse(setting2 == 8, "Hospitalised children and adults", setting),
         setting = ifelse(setting2 == 9, "Screening: hospitalised patients", setting),
         setting = ifelse(setting2 == 10, "Screening: general population", setting),
         setting = ifelse(setting2 == 11, "Screening: occupational", setting))
Q1_table$setting2 <- NULL

@@

settings=c("Contact investigation",
           "Contact investigation, aggregated",
           "Outbreak investigation",
           "Statistical model",
           "Screening",
           "Hospitalised adults",
           "Hospitalised children",
           "Hospitalised adults & children")

asymptomaticQ1$setting2<-factor(asymptomaticQ1$setting2, levels=1:8, labels=settings)
#combine contact investigation and contact investigation aggregated
asymptomaticQ1$setting2[asymptomaticQ1$setting2 == "Contact investigation, aggregated"] <- "Contact investigation"

@@

asymptomaticQ1$setting=asymptomaticQ1$setting2

@@

#change clusters to descriptions
asymptomaticQ1$label[asymptomaticQ1$label == "#4479 Harada [cluster:1]"] <- "#4479 Harada [Patients]"
asymptomaticQ1$label[asymptomaticQ1$label == "#4479 Harada [cluster:2]"] <- "#4479 Harada [Healthcare workers]"
#asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:1]"] <- "#2826 Taylor []" #clarify
#asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:2]"] <- "#2826 Taylor []"
asymptomaticQ1$label[asymptomaticQ1$label == "#2892 Kennelly [cluster:1]"] <- "#2892 Kennelly [Nursing home residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2892 Kennelly [cluster:2]"] <- "#2892 Kennelly [Nursing home staff]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2802 Bender [cluster:1]"] <- "#2802 Bender [Hospital 1]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2802 Bender [cluster:2]"] <- "#2802 Bender [Hospital 2]"
asymptomaticQ1$label[asymptomaticQ1$label == "#4968 van Buul [cluster:1]"] <- "#4968 van Buul [Nursing home residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#4968 van Buul [cluster:2]"] <- "#4968 van Buul [Healthcare workers]"
asymptomaticQ1$label[asymptomaticQ1$label == "#5273 Theuring [cluster:1]"] <- "#5273 Theuring [School students and staff]"
asymptomaticQ1$label[asymptomaticQ1$label == "#5273 Theuring [cluster:2]"] <- "#5273 Theuring [Household members]"

@@

@@

png(file = 'forest_meta_Q1.png',width=25,height=70, res=600, units="cm")

@@

![Box 1. Definitions of symptoms and symptom status in a person with SARS-CoV-2 infections](Box1.png)

>>>>

#clean settings
Q1_table <- Q1_table %>%
  mutate(setting = ifelse(setting2 == 1, "Contact investigation", setting),
         setting = ifelse(setting2 == 2, "Contact investigation, aggregated", setting),
         setting = ifelse(setting2 == 3, "Outbreak investigation", setting),
         setting = ifelse(setting2 == 4, "Statistical model", setting),
         setting = ifelse(setting2 == 5, "Screening", setting),
         setting = ifelse(setting2 == 6, "Hospitalised adults", setting),
         setting = ifelse(setting2 == 7, "Hospitalised children", setting),
         setting = ifelse(setting2 == 8, "Hospitalised children and adults", setting),
         setting = ifelse(setting2 == 9, "Screening: institutional setting", setting),
         setting = ifelse(setting2 == 10, "Screening: community setting", setting),
         setting = ifelse(setting2 == 11, "Screening: occupational", setting))
Q1_table$setting2 <- NULL

@@

settings=c("Contact investigation",
           "Contact investigation, aggregated",
           "Outbreak investigation",
           "Statistical model",
           "Screening",
           "Hospitalised adults",
           "Hospitalised children",
           "Hospitalised adults & children",
           "Screening: institutional setting",
           "Screening: community setting",
           "Screening: occupational")

asymptomaticQ1$setting2<-factor(asymptomaticQ1$setting2, levels=1:11, labels=settings)
#combine contact investigation and contact investigation aggregated
asymptomaticQ1$setting2[asymptomaticQ1$setting2 == "Contact investigation, aggregated"] <- "Contact investigation"

@@

asymptomaticQ1$setting = asymptomaticQ1$setting2

@@

#change clusters to descriptions
asymptomaticQ1$label[asymptomaticQ1$label == "#4479 Harada [cluster:1]"] <- "#4479 Harada [Patients]"
asymptomaticQ1$label[asymptomaticQ1$label == "#4479 Harada [cluster:2]"] <- "#4479 Harada [Healthcare workers]"
#asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:1]"] <- "#2826 Taylor []" #clarify
#asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:2]"] <- "#2826 Taylor []"
asymptomaticQ1$label[asymptomaticQ1$label == "#2892 Kennelly [cluster:1]"] <- "#2892 Kennelly [Nursing home residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2892 Kennelly [cluster:2]"] <- "#2892 Kennelly [Nursing home staff]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2802 Bender [cluster:1]"] <- "#2802 Bender [Hospital 1]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2802 Bender [cluster:2]"] <- "#2802 Bender [Hospital 2]"
asymptomaticQ1$label[asymptomaticQ1$label == "#4968 van Buul [cluster:1]"] <- "#4968 van Buul [Nursing home residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#4968 van Buul [cluster:2]"] <- "#4968 van Buul [Healthcare workers]"
asymptomaticQ1$label[asymptomaticQ1$label == "#5273 Theuring [cluster:1]"] <- "#5273 Theuring [School students and staff]"
asymptomaticQ1$label[asymptomaticQ1$label == "#5273 Theuring [cluster:2]"] <- "#5273 Theuring [Household members]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2751 van den Besselaar [cluster:1]"] <- "#2751 van den Besselaar [Healthcare workers]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2751 van den Besselaar [cluster:2]"] <- "#2751 van den Besselaar [Residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:1]"] <- "#2826 Taylor [Healthcare personnel]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:2]"] <- "#2826 Taylor [Residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#3719 Ladhani [cluster:1]"] <- "#3719 Ladhani [Residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#3719 Ladhani [cluster:2]"] <- "#3719 Ladhani [Healthcare workers]"
asymptomaticQ1$label[asymptomaticQ1$label == "#5551 Vohra [cluster:1]"] <- "#5551 Vohra [Presurgical patients]"
asymptomaticQ1$label[asymptomaticQ1$label == "#5551 Vohra [cluster:2]"] <- "#5551 Vohra [Undergoing chemotherapy]"
asymptomaticQ1$label[asymptomaticQ1$label == "#6526 Garibaldi [cluster:1]"] <- "#6526 Garibaldi [Residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#6526 Garibaldi [cluster:2]"] <- "#6526 Garibaldi [Staff]"

@@

#cut data at end of jan 31
data <- data[data$record_id <= 5296, ]

@@

png(file = 'forest_meta_Q1.png',width=25,height=80, res=600, units="cm")

@@
